\section{Preliminary}
\label{sec:pre}
\begin{definition}
\textbf{Distance-based similarity}. Given two objects $\bmx_i,\bmx_j \in R^d$,
the distance-based similarity measures their affinity based on the feature distance.
The measure should be symmetric and non-negative.
\hfill$\Box$
\end{definition}

\begin{example}
Gaussian kernel is a common choice, which has been widely used in spectral clustering. 
Given two objects $\bmx_i,\bmx_j$, 
$S_{ij} = exp(-\frac{||\bmx_i-\bmx_j||^2}{2\sigma^2})$,
where $||\cdot||$ denotes the standard Euclidean distance
and $\sigma$ is the scaling parameter.
\end{example}

\comment{
When the data contains multi-scale clusters,
there may not be a single value of $\sigma$ that works well for all the data.
In~\cite{zelnik2004self}, a measure considering local scaling is introduced.
}

\begin{example}
In the case of multi-scale clusters,
~\cite{zelnik2004self} calculates  
$S_{ij} = exp(-\frac{||\bmx_i-\bmx_j||^2}{\sigma_i\sigma_j})$,
where $\sigma_i,\sigma_j$ denote the local scaling parameters for objects $\bmx_i,\bmx_j$ respectively.
The local scaling parameters adjust the similarity between $\bmx_i$ and $\bmx_j$
according to local statistics of their neighborhoods.
\end{example}

Generally, the similarity between objects in the same cluster should be large 
while the similarity between objects in different clusters should be small. 
However, in the case of multi-scale data,
the distance-based similarity is likely to be abnormal.

\begin{definition}
\textbf{effective/Ineffective similarity}. 
Given two objects $\bmx_i$ and $\bmx_j$,
$S_{ij}$ is an effective similarity
if (1) $S_{ij}$ is large and $L(\bmx_i) = L(\bmx_j)$
or (2) $S_{ij}$ is small and $L(\bmx_i) \neq L(\bmx_j)$,
where $L(\cdot)$ denotes the true cluster label function.
Otherwise, $S_{ij}$ is an ineffective similarity
if (1) $S_{ij}$ is large but $L(\bmx_i) \neq L(\bmx_j)$
or (2) $S_{ij}$ is small but $L(\bmx_i) = L(\bmx_j)$.
\hfill$\Box$
\end{definition}

\begin{example}
In Fig.~\ref{figure:example1},
$S_{34}$ is an effective similarity because $\bmx_3$ and $\bmx_4$ belong to the same cluster 
and $S_{34}$ is large due to the short distance.
However, $S_{23}$ is an ineffective similarity because $\bmx_2$ and $\bmx_3$
have the same cluster label but they are far away from each other, leading to a small $S_{23}$.
Further, $S_{12}$ is also an ineffective similarity as $\bmx_1$ and $\bmx_2$ are in different clusters but with high similarity.
\end{example}









